Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-10-29 drafts/1spp.tex
Updates from Overleaf
some fairly minor changes today

\begin{itemize}
    \item Our experiment was conducted in a recirculating flume: water was propelled by an electric pump through a pipe of gradually increasing hydraulic diameter with a rectangular cross-section, through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure \ref{fig:floorplan}).
    \begin{itemize}
        \item channel depth: 40 cm, channel width: 60 cm, and test-section length: 2 m.
    \end{itemize}
    \item Our pump operated without cavitation in its chambers above 30 Hz, which corresponded to a flow velocity of 6 cm/s in the test section; we selected 10, 20, and 30 Hz as our velocity treatment levels to cover a suitable range of Reynolds numbers (67-200), and determined that flow velocity scaled linearly with pump frequency (Figure \ref{fig:freqvel}).
    \begin{itemize}
        \item \textcolor{violet}{Should this figure (\ref{fig:freqvel}) be cut? I kind of think so.}
    \end{itemize}

@@

\begin{itemize}
    \item Measurements taken by the ADV were filtered based on discrepancies between the two vertical velocity measurements, and despiked according to \cite{goring_nikora}.
    \item TKE and average velocity were calculated separately for each height $\times$ treatment combination:
\begin{equation}
    \text{TKE} = \frac{1}{2}(\overline{(u^\prime)^2} + \overline{(v^\prime)^2} + \overline{(w^\prime)^2})\,.
    \label{eqn:TKE}
\end{equation}

>>>>

\begin{itemize}
    \item Our experiment was conducted in a recirculating flume: water was propelled by an electric pump through a pipe of gradually increasing hydraulic diameter with a rectangular cross-section, through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure \ref{fig:floorplan}).
    \begin{itemize}
        \item channel depth: 40 cm, channel width: 60 cm, and test-section length: 1.95 m.
    \end{itemize}
    \item Our pump operated without cavitation in its chambers above 30 Hz, which corresponded to a flow velocity of 6 cm/s in the test section; we selected 10, 20, and 30 Hz as our velocity treatment levels to cover a suitable range of Reynolds numbers (67-200), and determined that flow velocity scaled linearly with pump frequency (Figure \ref{fig:freqvel}).
    \begin{itemize}
        \item \textcolor{violet}{Should this figure (\ref{fig:freqvel}) be cut? I kind of think so.}
    \end{itemize}

@@

\begin{itemize}
    \item 
    \item TKE and average velocity were calculated separately for each height $\times$ treatment combination:
\begin{equation}
    \text{TKE} = \frac{1}{2}(\overline{(u^\prime)^2} + \overline{(v^\prime)^2} + \overline{(w^\prime)^2})\,.
    \label{eqn:TKE}
\end{equation}

### 2020-10-29 drafts/draft.tex
some fairly minor changes today

Sediment capture in natural flows through vegetation have been described using a combination of physical mechanisms: gravitational settling, inertial impaction, diffusional deposition, and direct interception (REF papers that describe these phenomena). Sediment settles and deposits on the bed due to gravitational settling because sediment density is greater than that of water. Vegetation stems, often called ``collectors," can physically trap sediment on their surfaces. Inertial impaction and diffusional deposition are other means by which suspended particles can adhere to collectors (this sentence sounds vague, need to justify why we do not study inertial impaction and diffusional deposition, for example, which mechanisms dominate in transitional flows according to particle Reynolds number? If only direct intercept and gravitational settling matter, then that's our justification). Inertial impaction occurs when particles possess momentum relative to streamlines, and diffusional deposition arises due to some combination of turbulence and Brownian motion. Direct interception is the collision and adhesion of particles traveling along streamlines to the surfaces of collectors (e.g., plants). This is just one of several mechanisms that can remove particles from suspension (remove this sentence?). In this study, we focus on direct interception of suspended particles by emergent vegetation BECAUSE... (something about importance for transitional flows in vegetated shallow wetlands).

>>>>

Sediment capture in natural flows through vegetation has been described using a combination of physical mechanisms: gravitational settling, inertial impaction, diffusional deposition, and direct interception (REF papers that describe these phenomena). Sediment settles and deposits on the bed due to gravitational settling because sediment density is greater than that of water. Vegetation stems, often called ``collectors," can physically trap sediment on their surfaces. Inertial impaction and diffusional deposition are other means by which suspended particles can adhere to collectors (this sentence sounds vague, need to justify why we do not study inertial impaction and diffusional deposition, for example, which mechanisms dominate in transitional flows according to particle Reynolds number? If only direct intercept and gravitational settling matter, then that's our justification). Inertial impaction occurs when particles possess momentum relative to streamlines, and diffusional deposition arises due to some combination of turbulence and Brownian motion. Direct interception is the collision and adhesion of particles traveling along streamlines to the surfaces of collectors (e.g., plants). This is just one of several mechanisms that can remove particles from suspension (remove this sentence?). In this study, we focus on direct interception of suspended particles by emergent vegetation BECAUSE... (something about importance for transitional flows in vegetated shallow wetlands).
